---
title: "Investigate FR07961003 sample"
date: "`r Sys.Date()`"
author: "J. Boom"
format:
    html:
        toc: true
        self-contained: true
        toc-title: Table of contents - Investigate FR07961003 sample
        toc-location: left
execute:
    echo: true
---

# Load packages
```{r}
#| warning: false

library("tidyverse")
library("knitr")
library("readxl")
library("broom")
library("naniar")
library("factoextra")
library("FactoMineR")
library("plotROC")
library("data.table")
library("Rtsne")
library("cutpointr")
```

# Run document setup
```{r}
#| warning: false

# Set a seed for reproducability.
set.seed(1995)

# Set other formatting settings of Quarto document.
knitr::opts_chunk$set(echo=TRUE,
                      message=FALSE,
                      fig.width=9,
                      fig.height=9,
                      out.width="85%",
                      fig.align="center")

# Set a nice theme.
theme_set(theme_bw())
```

# UK Personal Genome project
## Load datasets for individual FR07961003
```{r}
#| warning: false

# Read in the tsv file in the data folder, based on the personal genome project.
# This is individual FR07961003. It includes the variants from the GIAB/ClinVar
# test set.
FR07961003 <- read_tsv(
    "/mnt/titan/users/j.boom/vcf/personalgenomesuk/FR07961003.pass.recode.annotated.edit.tab",
    col_names=TRUE,
    show_col_types = FALSE)
```

## Inspect & select data for individual FR07961003
```{r}
#| label: tbl-data
#| tbl-cap: _The first 8 rows of the most important numeric annotations._
#| warning: false

# Condense rows to one per variation id, vep reports all transcripts it can
# find by default.
FR07961003.dedup <- FR07961003[!duplicated(
    FR07961003$`Uploaded_variation`), ] |>
    dplyr::rename("Variation_id" = 1)

# Select just the important numeric annotation sources. Replace dash with NA
# and make sure the values are numeric.
FR07961003.select <- FR07961003.dedup[, c("Variation_id",
                                          "CADD_PHRED",
                                          "CADD_RAW",
                                          "CAPICE_SCORE",
                                          "FATHMM_MKL_C",
                                          "FATHMM_MKL_NC",
                                          "ClinVar_CLNSIG")] |>
    replace_with_na_all(condition = ~.x == "-") |>
    mutate_at(c("CADD_PHRED",
                "CADD_RAW",
                "CAPICE_SCORE",
                "FATHMM_MKL_C",
                "FATHMM_MKL_NC"),
              function(x) as.numeric(as.character(x)))

# Remove rows of columns with missing values, set the category to a factor and
# set the variant identifiers as rownames.
FR07961003.nomissing <- FR07961003.select |>
    drop_na() |>
    dplyr::mutate_at(c("ClinVar_CLNSIG"),
                     as.factor) |>
    tibble::column_to_rownames(var="Variation_id")

# Display the first 8 lines of the data.
head(FR07961003.nomissing,
     n=8) |>
    knitr::kable(format="html") |>
    kableExtra::kable_classic(full_width=FALSE)
```

## Run PCA package for individual FR07961003
```{r}
#| warning: false

# http://www.sthda.com/english/wiki/factoextra-r-package-
# easy-multivariate-data-analyses-and-elegant-visualization
# Perform a principal component analysis, include centering and scaling of data.
# Using the PCA command.
FR07961003.pca.data <- PCA(FR07961003.nomissing[,1:5],
                           graph=FALSE,
                           ncp=4,
                           scale.unit=TRUE)

# Extract the results for variables.
FR07961003.pca.var <- get_pca_var(FR07961003.pca.data)

# Contributions of variables to PC1.
FR07961003.pc1.contribs <- fviz_contrib(FR07961003.pca.data,
                                        choice="var",
                                        axes=1,
                                        top=10)

# Contributions of variables to PC2.
FR07961003.pc2.contribs <- fviz_contrib(FR07961003.pca.data,
                                        choice="var",
                                        axes=2,
                                        top=10)
```

## Run prcomp package for individual FR07961003
```{r}
#| warning: false

# https://plotly.com/ggplot2/pca-visualization/
# Perform a principal component analysis, include centering and scaling of data.
# Using the prcomp command.
FR07961003.prcomp.data <- prcomp(
    FR07961003.nomissing[,1:5],
    center=TRUE,
    scale.=TRUE)
```

## Create a scatterplot for individual FR07961003
```{r}
#| warning: false

# Prepare data from prcomp for ggplot scatterplot.
FR07961003.pca.scatterplot.data <- cbind(
    FR07961003.prcomp.data$x[,1:2],
    as.character(FR07961003.nomissing[,6])) |>
    as_tibble() |>
    dplyr::rename(PC1="PC1",
                  PC2="PC2",
                  CONDITION="V3") |>
    dplyr::mutate_at(c("PC1"),
                     as.numeric) |>
    dplyr::mutate_at(c("PC2"),
                     as.numeric) |>
    dplyr::arrange(CONDITION)

# Extract the variance explained by the first two components.
FR07961003.pca.variance <- summary(
    FR07961003.prcomp.data)$importance[2,]

# Create the scatterplot.
FR07961003.pca.scatterplot <- ggplot(
    data=FR07961003.pca.scatterplot.data,
    aes(x=PC1,
        y=PC2,
        colour=CONDITION)) +
    geom_point(size=2) +
    theme(legend.position=c(0.95,0.75),
          legend.justification=c(1,0)) +
    scale_colour_manual(values=c("#83b96d",
                                 "#00a6cf"),
                        name="Clinical significance") +
    ggtitle("Projection of data on principal components one and two") +
    xlab(paste(paste("PC1 -",
                     format(round(FR07961003.pca.variance["PC1"] * 100),
                            2,
                            nsmall=2),
                     sep=" "),
               "%",
               sep="")) +
    ylab(paste(paste("PC2 -",
                     format(round(FR07961003.pca.variance["PC2"] * 100),
                            2,
                            nsmall=2),
                     sep=" "),
               "%",
               sep=""))

# Print the scatterplot.
FR07961003.pca.scatterplot
```

## Create a barplot for individual FR07961003
```{r}
#| warning: false

# Prepare data from prcomp for ggplot barplot.
FR07961003.pca.barplot.data <- cbind(FR07961003.pc1.contribs$data[,c(1,2)],
                                     FR07961003.pc2.contribs$data[,2]) |>
    as_tibble() |>
    dplyr::rename(PC1="contrib",
                  PC2="FR07961003.pc2.contribs$data[, 2]",
                  METHOD="name") |>
    dplyr::mutate_at(c("PC1"), as.numeric) |>
    dplyr::mutate_at(c("PC2"), as.numeric) |>
    pivot_longer(names_to="PCA",
                 values_to="CONTRIBUTION",
                 cols=c("PC1", "PC2")) |>
    dplyr::mutate(across(c("CONTRIBUTION"),
                         round,
                         2))

# Create the barplot.
FR07961003.pca.barplot <- ggplot(data=FR07961003.pca.barplot.data,
                                 aes(x=METHOD,
                                     y=CONTRIBUTION,
                                     fill=PCA,
                                     colour=PCA)) +
    ylim(c(0,70)) +
    geom_bar(stat="identity",
             position=position_dodge()) +
    geom_text(aes(label=CONTRIBUTION),
              fontface="bold",
              vjust=-1,
              position=position_dodge(0.9),
              size=4,
              colour="black") +
    theme(legend.position=c(0.95,0.75),
          legend.justification=c(1,0)) +
    scale_colour_manual(values=c("#003670",
                                 "#ec9e62"),
                        name="Principal component") +
    scale_fill_manual(values=c("#003670",
                               "#ec9e62"),
                      name="Principal component") +
    ggtitle("Contribution of the different annotation sources in principal\
             components one and two") +
    xlab("Annotation source") +
    ylab("Contribution (%)")

# Print the barplot.
FR07961003.pca.barplot
```

## Create scatterplot using the annotation scores for individual FR07961003
```{r}
#| warning: false

# Create a scatterplot of purely the scores we got from CAPICE and FATHMM
# coding.
FR07961003.scores.scatterplot <- ggplot(
    data=FR07961003.nomissing,
    aes(x=CAPICE_SCORE,
        y=FATHMM_MKL_C,
        colour=ClinVar_CLNSIG)) +
    geom_point(size=2) +
    theme(legend.position=c(0.6,0.2),
          legend.justification=c(1,0)) +
    scale_colour_manual(values=c("#83b96d",
                                 "#003670"),
                        name="Clinical significance") +
    ggtitle("Annotation scores from CAPICE and FATHMM coding") +
    xlab("CAPICE source") +
    ylab("FATHMM coding score")

# Print the scatterplot.
FR07961003.scores.scatterplot
```

## Create TSNE plot for individual FR07961003
```{r}
#| warning: false

# https://plotly.com/ggplot2/pca-visualization/
# Create a TSNE object using the annotation columns, make sure to ignore
# duplicates, this has something to do with identical values generated by the
# PCA which is done under the hood.
FR07961003.tsne <- Rtsne(
    as.matrix(FR07961003.nomissing[,1:5]),
    check_duplicates=FALSE)

# Extract the coordinates created by TSNE and add a column for colouring.
FR07961003.tsne.data <- data.frame(
    x=FR07961003.tsne$Y[,1],
    y=FR07961003.tsne$Y[,2],
    colour=FR07961003.nomissing$ClinVar_CLNSIG)
```

## Display the TSNE plot
```{r}
#| warning: false

# Use ggplot to display the TSNE results.
FR07961003.tsne.plot <- ggplot(
    data=FR07961003.tsne.data,
    aes(x=x,
        y=y,
        colour=colour)) +
    geom_point(size=2) +
    scale_colour_manual(values=c("#ec9e62",
                                 "#00a6cf"),
                        name="Clinical significance") +
    ggtitle("TSNE clustering of all annotation sources") +
    xlab("") +
    ylab("")

# Print the TSNE plot.
FR07961003.tsne.plot
```

# Create a random subset and assign random conditions
```{r}
#| warning: false

# Create one subsets with a size of 10000 variants.
FR07961003.set.1 <- FR07961003.nomissing |>
    sample_n(10000) |>
    dplyr::select(-ClinVar_CLNSIG)

# Create a vector with the possible conditions for variants.
CONDITION <- c("Benign", "Pathogenic")

# Assign the conditions set in the vector above randomly to all variants,
# making sure we get 5000 of each.
FR07961003.set.1$CONDITION[sample(1:nrow(FR07961003.set.1),
                                  nrow(FR07961003.set.1),
                                  FALSE)] <- rep(CONDITION,
                                                 c(5000,
                                                   5000))
```

## Create a ROC plot based on the random dataset
```{r}
#| warning: false

# https://cran.r-project.org/web/packages/plotROC/vignettes/examples.html
# Use ggplot and plotROC to create ROC plots for each annotation source.
FR07961003.set.1.combined.roc.plots <- ggplot(
    melt_roc(FR07961003.set.1,
             "CONDITION",
             c("CADD_PHRED",
               "CADD_RAW",
               "CAPICE_SCORE",
               "FATHMM_MKL_C",
               "FATHMM_MKL_NC")),
    aes(m=M,
        d=D,
        colour=name)) +
    geom_roc(n.cuts=5,
             labelsize=5,
             labelround=2,
             show.legend=TRUE,
             labels=FALSE) +
    xlim(-0.1, 1) +
    ylim(0, 1.1)

FR07961003.set.1.combined.roc.plots +
    facet_wrap(~ name)

# Calculate the AUC of each ROC plot.
calc_auc(FR07961003.set.1.combined.roc.plots) |>
    knitr::kable(format="html") |>
    kableExtra::kable_classic(full_width=FALSE)
```

## Run prcomp for the random set
```{r}
#| warning: false

# https://plotly.com/ggplot2/pca-visualization/
# Perform a principal component analysis, include centering and scaling of data.
# Using the prcomp command.
FR07961003.set.1.prcomp.data <- prcomp(
    FR07961003.set.1[,1:5],
    center=TRUE,
    scale.=TRUE)
```

## Create a scatterplot for the random set
```{r}
#| warning: false

# Prepare data from prcomp for ggplot scatterplot.
FR07961003.set.1.pca.scatterplot.data <- cbind(
    FR07961003.set.1.prcomp.data$x[,1:2],
    as.character(FR07961003.set.1[,6])) |>
    as_tibble() |>
    dplyr::rename(PC1="PC1",
                  PC2="PC2",
                  CONDITION="V3") |>
    dplyr::mutate_at(c("PC1"),
                     as.numeric) |>
    dplyr::mutate_at(c("PC2"),
                     as.numeric) |>
    dplyr::arrange(CONDITION)

# Extract the variance explained by the first two components.
FR07961003.set.1.pca.variance <- summary(
    FR07961003.set.1.prcomp.data)$importance[2,]

# Create the scatterplot.
FR07961003.set.1.pca.scatterplot <- ggplot(
    data=FR07961003.set.1.pca.scatterplot.data,
    aes(x=PC1,
        y=PC2,
        colour=CONDITION)) +
    geom_point(size=2) +
    theme(legend.position=c(0.99,0.01),
          legend.justification=c(1,0)) +
    scale_colour_manual(values=c("#83b96d",
                                 "#00a6cf"),
                        name="Clinical significance") +
    ggtitle("Projection of data on principal components one and two") +
    xlab(paste(paste("PC1 -",
                     format(round(FR07961003.set.1.pca.variance["PC1"] * 100),
                            2,
                            nsmall=2),
                     sep=" "),
               "%",
               sep="")) +
    ylab(paste(paste("PC2 -",
                     format(round(FR07961003.set.1.pca.variance["PC2"] * 100),
                            2,
                            nsmall=2),
                     sep=" "),
               "%",
               sep=""))

# Print the scatterplot.
FR07961003.set.1.pca.scatterplot
```

# Use the cutpointr package for creating ROC plots
```{r}
#| warning: false

# Create the ROC objects with all required information.
## CADD_PHRED.
FR07961003.cp.CADD_PHRED <- cutpointr(
    FR07961003.nomissing,
    CADD_PHRED,
    ClinVar_CLNSIG,
    method=maximize_metric,
    metric=sum_sens_spec,
    pos_class="Pathogenic",
    neg_class="Benign",
    silent=TRUE)

## CADD_RAW.
FR07961003.cp.CADD_RAW <- cutpointr(
    FR07961003.nomissing,
    CADD_RAW,
    ClinVar_CLNSIG,
    method=maximize_metric,
    metric=sum_sens_spec,
    pos_class="Pathogenic",
    neg_class="Benign",
    silent=TRUE)

## CAPICE_SCORE.
FR07961003.cp.CAPICE_SCORE <- cutpointr(FR07961003.nomissing,
                                        CAPICE_SCORE,
                                        ClinVar_CLNSIG,
                                        method=maximize_metric,
                                        metric=sum_sens_spec,
                                        pos_class="Pathogenic",
                                        neg_class="Benign",
                                        silent=TRUE)

## FATHMM_MKL_C.
FR07961003.cp.FATHMM_MKL_C <- cutpointr(FR07961003.nomissing,
                                        FATHMM_MKL_C,
                                        ClinVar_CLNSIG,
                                        method=maximize_metric,
                                        metric=sum_sens_spec,
                                        pos_class="Pathogenic",
                                        neg_class="Benign",
                                        silent=TRUE)

## FATHMM_MKL_NC.
FR07961003.cp.FATHMM_MKL_NC <- cutpointr(FR07961003.nomissing,
                                         FATHMM_MKL_NC,
                                         ClinVar_CLNSIG,
                                         method=maximize_metric,
                                         metric=sum_sens_spec,
                                         pos_class="Pathogenic",
                                         neg_class="Benign",
                                         silent=TRUE)
```

## Prepare the data for plotting ROC lines
```{r}
#| warning: false

# Prepare the data for plotting the ROC line.
FR07961003.cp.CADD_PHRED.roc <- as.data.frame(
    FR07961003.cp.CADD_PHRED[["roc_curve"]]) |>
    mutate(annotation = "CADD_PHRED")
FR07961003.cp.CADD_RAW.roc <- as.data.frame(
    FR07961003.cp.CADD_RAW[["roc_curve"]]) |>
    mutate(annotation = "CADD_RAW")
FR07961003.cp.CAPICE_SCORE.roc <- as.data.frame(
    FR07961003.cp.CAPICE_SCORE[["roc_curve"]]) |>
    mutate(annotation = "CAPICE_SCORE")
FR07961003.cp.FATHMM_MKL_C.roc <- as.data.frame(
    FR07961003.cp.FATHMM_MKL_C[["roc_curve"]]) |>
    mutate(annotation = "FATHMM_MKL_C")
FR07961003.cp.FATHMM_MKL_NC.roc <- as.data.frame(
    FR07961003.cp.FATHMM_MKL_NC[["roc_curve"]]) |>
    mutate(annotation = "FATHMM_MKL_NC")

## Combine all tables.
FR07961003.cp.roc.data <- rbind(FR07961003.cp.CADD_PHRED.roc,
                                FR07961003.cp.CADD_RAW.roc,
                                FR07961003.cp.CAPICE_SCORE.roc,
                                FR07961003.cp.FATHMM_MKL_C.roc,
                                FR07961003.cp.FATHMM_MKL_NC.roc)
```

## Also extract the optimal thresholds for classification
```{r}
#| warning: false

# Prepare the data for plotting the thresholds in the ROC plots.
## CADD_PHRED.
FR07961003.cp.roc.CADD_PHRED.threshold <- as.data.frame(
    FR07961003.cp.CADD_PHRED[["optimal_cutpoint"]]) |>
    mutate(annotation = "CADD_PHRED") |>
    rename(threshold = 1)
FR07961003.cp.roc.CADD_PHRED.threshold.location <- FR07961003.cp.CADD_PHRED.roc[
    FR07961003.cp.CADD_PHRED.roc$x.sorted == FR07961003.cp.CADD_PHRED[["optimal_cutpoint"]],][,c(
        "x.sorted",
        "fpr",
        "tpr")] |>
    rename(threshold = 1)
FR07961003.cp.roc.CADD_PHRED.threshold.location.total <- merge(
    FR07961003.cp.roc.CADD_PHRED.threshold,
    FR07961003.cp.roc.CADD_PHRED.threshold.location,
    by="threshold")

## CADD_RAW.
FR07961003.cp.roc.CADD_RAW.threshold <- as.data.frame(
    FR07961003.cp.CADD_RAW[["optimal_cutpoint"]]) |>
    mutate(annotation = "CADD_RAW") |>
    rename(threshold = 1)
FR07961003.cp.roc.CADD_RAW.threshold.location <- FR07961003.cp.CADD_RAW.roc[
    FR07961003.cp.CADD_RAW.roc$x.sorted == FR07961003.cp.CADD_RAW[["optimal_cutpoint"]],][,c(
        "x.sorted",
        "fpr",
        "tpr")] |>
    rename(threshold = 1)
FR07961003.cp.roc.CADD_RAW.threshold.location.total <- merge(
    FR07961003.cp.roc.CADD_RAW.threshold,
    FR07961003.cp.roc.CADD_RAW.threshold.location,
    by="threshold")

## CAPICE_SCORE.
FR07961003.cp.roc.CAPICE_SCORE.threshold <- as.data.frame(
    FR07961003.cp.CAPICE_SCORE[["optimal_cutpoint"]]) |>
    mutate(annotation = "CAPICE_SCORE") |>
    rename(threshold = 1)
FR07961003.cp.roc.CAPICE_SCORE.threshold.location <- FR07961003.cp.CAPICE_SCORE.roc[
    FR07961003.cp.CAPICE_SCORE.roc$x.sorted == FR07961003.cp.CAPICE_SCORE[["optimal_cutpoint"]],][,c(
        "x.sorted",
        "fpr",
        "tpr")] |>
    rename(threshold = 1)
FR07961003.cp.roc.CAPICE_SCORE.threshold.location.total <- merge(
    FR07961003.cp.roc.CAPICE_SCORE.threshold,
    FR07961003.cp.roc.CAPICE_SCORE.threshold.location,
    by="threshold")

## FATHMM_MKL_C.
FR07961003.cp.roc.FATHMM_MKL_C.threshold <- as.data.frame(
    FR07961003.cp.FATHMM_MKL_C[["optimal_cutpoint"]]) |>
    mutate(annotation = "FATHMM_MKL_C") |>
    rename(threshold = 1)
FR07961003.cp.roc.FATHMM_MKL_C.threshold.location <- FR07961003.cp.FATHMM_MKL_C.roc[
    FR07961003.cp.FATHMM_MKL_C.roc$x.sorted == FR07961003.cp.FATHMM_MKL_C[["optimal_cutpoint"]],][,c(
        "x.sorted",
        "fpr",
        "tpr")] |>
    rename(threshold = 1)
FR07961003.cp.roc.FATHMM_MKL_C.threshold.location.total <- merge(
    FR07961003.cp.roc.FATHMM_MKL_C.threshold,
    FR07961003.cp.roc.FATHMM_MKL_C.threshold.location,
    by="threshold")

## FATHMM_MKL_NC.
FR07961003.cp.roc.FATHMM_MKL_NC.threshold <- as.data.frame(
    FR07961003.cp.FATHMM_MKL_NC[["optimal_cutpoint"]]) |>
    mutate(annotation = "FATHMM_MKL_NC") |>
    rename(threshold = 1)
FR07961003.cp.roc.FATHMM_MKL_NC.threshold.location <- FR07961003.cp.FATHMM_MKL_NC.roc[
    FR07961003.cp.FATHMM_MKL_NC.roc$x.sorted == FR07961003.cp.FATHMM_MKL_NC[["optimal_cutpoint"]],][,c(
        "x.sorted",
        "fpr",
        "tpr")] |>
    rename(threshold = 1)
FR07961003.cp.roc.FATHMM_MKL_NC.threshold.location.total <- merge(
    FR07961003.cp.roc.FATHMM_MKL_NC.threshold,
    FR07961003.cp.roc.FATHMM_MKL_NC.threshold.location,
    by="threshold")

## Combine all tables.
FR07961003.cp.roc.thresholds <- rbind(
    FR07961003.cp.roc.CADD_PHRED.threshold.location.total,
    FR07961003.cp.roc.CADD_RAW.threshold.location.total,
    FR07961003.cp.roc.CAPICE_SCORE.threshold.location.total,
    FR07961003.cp.roc.FATHMM_MKL_C.threshold.location.total,
    FR07961003.cp.roc.FATHMM_MKL_NC.threshold.location.total)
```

## Display the ROC plots
```{r}
#| warning: false

# Create ROC plots for the annotation sources, split over multiple windows.
FR07961003.lineplot <- ggplot(data=FR07961003.cp.roc.data,
                              aes(x=fpr,
                                  y=tpr,
                                  colour=annotation)) +
    geom_line() +
    geom_point(data=FR07961003.cp.roc.thresholds,
               aes(x=fpr,
                   y=tpr,
                   col=annotation)) +
    geom_text(data=FR07961003.cp.roc.thresholds,
              aes(x=fpr,
                  y=tpr,
                  label=threshold),
              vjust=2,
              hjust=-0.25) +
    theme(legend.position=c(0.95,0.001),
          legend.justification=c(1,0)) +
    scale_colour_manual(values=c("#ec9e62",
                                 "#00a6cf",
                                 "#83b96d",
                                 "#003670",
                                 "#C73B1D"),
                        name="Annotation source") +
    ggtitle("Receiver Operating Curves based on the five annotation\
             score sets") +
    xlab("False Positive Rate") +
    ylab("True Positive Rate") +
    xlim(-0.1, 1) +
    ylim(0, 1.1)

## Change the title of all plots.
FR07961003.lineplot.facet.titles <- c(
    paste("CADD PHRED - AUC:", substr(
        as.character(FR07961003.cp.CADD_PHRED$AUC), 1, 6)),
    paste("CADD RAW - AUC:", substr(
        as.character(FR07961003.cp.CADD_RAW$AUC), 1, 6)),
    paste("CAPICE SCORE - AUC:", substr(
        as.character(FR07961003.cp.CAPICE_SCORE$AUC), 1, 6)),
    paste("FATHMM MKL C - AUC:", substr(
        as.character(FR07961003.cp.FATHMM_MKL_C$AUC), 1, 6)),
    paste("FATHMM MKL NC - AUC:", substr(
        as.character(FR07961003.cp.FATHMM_MKL_NC$AUC), 1, 6)))

## Add names to the vector.
names(FR07961003.lineplot.facet.titles) <- c(
    "CADD_PHRED",
    "CADD_RAW",
    "CAPICE_SCORE",
    "FATHMM_MKL_C",
    "FATHMM_MKL_NC")

## Display the windowed ROC plots.
FR07961003.lineplot +
    facet_wrap(. ~ annotation,
               labeller=labeller(annotation=FR07961003.lineplot.facet.titles))
```

# Try out thresholds on individual FRO7961003
```{r}
#| warning: false

# Create a vector with the optimal thresholds, just as a reminder.
MODEL.THRESHOLDS <- c(
    21.5,
    2.21509,
    0.0089,
    0.71714,
    0.93525
)

# Select the variants that would classify as pathogenic.
FR07961003.validation.pathogenic <- FR07961003.nomissing[
    FR07961003.nomissing$CADD_PHRED > 21.5 &
    FR07961003.nomissing$CADD_RAW > 2.21509 &
    FR07961003.nomissing$CAPICE_SCORE > 0.0089 &
    FR07961003.nomissing$FATHMM_MKL_C > 0.71714 &
    FR07961003.nomissing$FATHMM_MKL_NC > 0.93525
,] |>
    mutate(MODEL = "Pathogenic")

# Select the variants that would classify as benign.
FR07961003.validation.benign <- FR07961003.nomissing[
    FR07961003.nomissing$CADD_PHRED <= 21.5 &
    FR07961003.nomissing$CADD_RAW <= 2.21509 &
    FR07961003.nomissing$CAPICE_SCORE <= 0.0089 &
    FR07961003.nomissing$FATHMM_MKL_C <= 0.71714 &
    FR07961003.nomissing$FATHMM_MKL_NC <= 0.93525
,] |>
    mutate(MODEL = "Benign")

# Combine the two subsets, now including a column with the classification.
FR07961003.validation.total <- rbind(
    FR07961003.validation.pathogenic,
    FR07961003.validation.benign
)

# Output a simple confusion matrix.
table(
    factor(FR07961003.validation.total$ClinVar_CLNSIG),
    factor(FR07961003.validation.total$MODEL)
) |>
    knitr::kable(format="html") |>
    kableExtra::kable_classic(full_width=FALSE)
```

# Output session information
```{r}
#| warning: false

# Print the session info including packages and version used.
sessionInfo()
```